### 2012-08-01 trunk/ijcis-pos-model/sources/preliminaries.tex
preprint version

%Introductory text:
In this section, we introduce some basic concepts concerning possibilistic variables and fuzzy numbers and intervals. Then, the framework of set evaluation by ill-known constraints \cite{Pons2011} is explained. The section concludes with a brief introduction to temporal databases.

@@

\subsection{\label{subsec:possibility-theory}Possibility Theory}
Possibility theory is devoted to the handling of incomplete information. In order to capture partial ignorance, two measures are provided: possibility and necessity.

\begin{definition}
Consider a set of outcomes $\Omega$. Let $\wp(\Omega)$ denote the powerset of $\Omega$ and let $A$ and $B$ be elements of $\wp(\Omega)$. A \emph{confidence measure on $\Omega$} is defined by a function
	\begin{align}
	g : \wp(\Omega) & \rightarrow \left[0,1\right]
	\end{align}
that satisfies
	\begin{align}
	g(\emptyset) &= 0 \\
	g(\Omega) &= 1 	\label{NormalizationProperty} \\
	A \subseteq B &\Rightarrow g(A) \leq g(B) \label{MonotonicityProperty}
	\end{align}
\end{definition}

Both possibility and necessity measures are special cases of confidence measures.

\begin{definition}
Consider a confidence measure $\Pi$ on a set of outcomes $\Omega$. Let $J$ be a countable index set and let $\{ A_{j} | j \in J \wedge A_{j} \subseteq \Omega \}$ be a family of elements of $\wp(\Omega)$. $\Pi$ is now a \emph{possibility measure on $\Omega$} if it satisfies:
	\begin{align}
	\Pi\left(\bigcup_{j \in J} A_{j} \right) = \sup_{j \in J} \Pi(A_{j})
	\end{align}
\end{definition}

In this work, the interpretation is as follows. The possibility of an event expresses how plausible the occurrence of the event seems to an observer of the experiment, given the (partial) knowledge of the observer about the experiment.

Information on the possibility of distinct elements of the universe of discourse $\Omega$ can now be given by a \emph{possibility distribution} $\pi$ on $\Omega$, defined by:

\begin{definition}
Consider a possibility measure $\Pi$ on $\Omega$. A \emph{possibility distribution} $\pi$ on $\Omega$ underlying the possibility measure $\Pi$ is a function defined by:
	\begin{align}
	\pi : \Omega \rightarrow \left[0, 1\right] : \pi(u) = \Pi(\{u\})
	\end{align}
\end{definition}

\begin{definition}
Consider a confidence measure $N$ on $\Omega$. Let $J$ be a countable index set and let $\{ A_{j} | j \in J \wedge A_{j} \subseteq \Omega \}$ be a family of elements of $\wp(\Omega)$. $N$ is a \emph{necessity measure} on $\Omega$ if it satisfies:
	\begin{align}
	N\left(\bigcap_{j \in J} A_{j} \right) = \inf_{j \in J} N(A_{j})
	\end{align}
\end{definition}

In this work, the interpretation is as follows. The necessity of an event expresses how necessary the occurrence of the event seems to an observer of the experiment, given the (partial) knowledge of the observer about the experiment.

Possibility and necessity measures are dual in the sense that:

\begin{align}
\forall A \subseteq \Omega : N(A) = 1 - \Pi(\bar{A})
\end{align}

That is, the degree to which an event is necessary is the extent to every other possible event is not plausible.

\subsection{\label{subsec:possibilistic-variables}Possibilistic Variables}
Possibilistic variables rely on possibility theory \cite{Dubois1988a} and are defined as follows \cite{Pons2011}.

\begin{definition}
\label{def;possibilistic-variable}
A possibilistic variable $X$ over a universe $U$ is defined as a variable taking exactly one value in $U$, but for which this value is (partially) unknown. Possibility distribution $\pi_X$ on $U$ models the available knowledge about the value $X$ takes; for each $u\in U$, $\pi_X(u)$ represents the possibility that $X$ takes the value $u$. In this work, this possibility is interpreted as a measure of how plausible it is that $X$ takes the value $u$, given (partial) knowledge about the value $X$ takes.
\end{definition}

The exact value a possibilistic variable takes, which is (partially) unknown, is called an \emph{ill-known value} in this work \cite{Dubois1988a}.

When a possibilistic variable is defined on the powerset $\Pow(U)$ of some universe $U$, the unique value the variable takes will be a crisp set and its possibility distribution on the powerset $\Pow(U)$ will describe the possibility of each crisp subset of $U$ to be the value the variable takes. This exact value (a crisp set) the variable takes, is now called an \emph{ill-known set} \cite{Dubois1988a}.

% It is important to understand the difference between the following two concepts:
% \begin{itemize}
% \item
% A \emph{possibilistic variable} $X$ is bounded to take only one value , but this value is not known due to incomplete knowledge. 
% \item
% An \emph{ill-known set}~\cite{Dubois1988a}: a possibilistic variable defined over the universe $\Pow(U)$.
% \end{itemize}

Note that while a single ill-known value refers to one (partially) unknown value, an ill-known set is a crisp set but, for some reason, (partially) unknown.

A specific application of possibilistic variables is obtained when the universe under consideration is the set of Boolean values $\mathbb{B}$ = $\{T,F\}$. Indeed, any Boolean proposition $p$ takes just one value in $\mathbb{B}$. If the knowledge about which value this proposition $p$ will take is given by a possibility distribution $\pi_p$; the proposition can be seen as a possibilistic variable. The possibility and necessity that $p$ = $T$ (the proposition holds) demand more attention. This possibility and necessity is noted here as:
\begin{align}
\label{propholdsposs}
\text{Possibility that $p$ = $T$ (p holds):} &\\
\nonumber
Pos(p) = \pi_p(T)  \\
\label{propholdsnecc}
\text{Necessity that $p$ = $T$ (p holds):} & \\
\nonumber
Nec(p) = 1-\pi_p(F) 
\end{align}

Here, equation \eqref{propholdsposs} denotes the possibility that $p$ = $T$ and the proposition holds, while equation \eqref{propholdsnecc} denotes the necessity that $p$ = $T$ and the proposition holds.

This work deals with ill-known intervals. These are ill-known sets, defined and represented via a starting and ending points that, in turn are ill-known values. The elements of the set are the values between the starting and ending points. A closed ill-known interval with starting point defined by possibilistic variable $X$ and ending point by possibilistic variable $Y$ is noted here $\left[X, Y\right]$. %The correspondences and transitions between the representations of ill-known sets, between the representations of ill-known intervals and between the representations of an ill-known set and an ill-known interval are part of the authors current research.

\subsection{\label{subsec:fuzzy-numbers}Fuzzy Numbers and Fuzzy Intervals}
Among others, Dubois and Prade~\cite{Dubois1983} use fuzzy sets \cite{Zadeh1965} to define a \emph{fuzzy interval}:
\begin{definition}
A fuzzy interval is a fuzzy set $M$, defined by a membership function $\mu_{M}$ on the set of real numbers $\mathbb{R}$ such that:
\begin{eqnarray}
\mu_{M} :  \mathbb{R} \rightarrow \left[0,1\right]  \\ 
\nonumber
\forall (u,v)\in\mathbb{R}^2: \forall w \in [u,v]:\\
\nonumber
\mu_M(w) \geq\min(\mu_M(u),\mu_M(v))  \\
\nonumber
\exists m \in \mathbb{R} :  \mu_M(m)=1 
\end{eqnarray}
\end{definition}

\begin{samepage}
\vspace*{13pt}
\begin{center}
{
\includegraphics[scale=0.25]{./graphs/triangular.pdf}

}
\end{center}
%\centerline{ \psfig{file=./graphs/Y-time-point.eps}}
\vspace*{10pt}
\fcaption{\label{fig:triangular-dist}Example of fuzzy number.}
%  \label{fig:fuzzy-validity-period}
\vspace*{13pt}
\end{samepage}
If this modal value $m$ is unique, then $M$ is referred to as a \emph{fuzzy number}. 
%In other words, if the core of a fuzzy interval is a singleton, it is referred to as a fuzzy number (Figure \ref{fig:triangular-dist}).

A simple form of the membership function of a fuzzy interval is a trapezoidal function (Figure \ref{fig:trapezoidal-dist}). It can be shown that such a membership function $\mu_T$ for a fuzzy interval $T$ is convex and normalized. The values $\left[\alpha, \beta, \gamma, \delta\right]$ represent a trapezoidal possibility distribution defined by $\mu_T$:

% Four real values, denoted $\alpha$, $\beta$, $\gamma$ and $\delta$ suffice to represent a trapezoidal membership function of a fuzzy interval. In this work, a fuzzy interval defined as such will be noted as . The corresponding membership function definition for this  is then given by:

\begin{align}
\mu_T : & \quad \mathbb{R} \rightarrow \left[0,1\right] \\
\nonumber
 : & \quad x \rightarrow
\begin{cases}
1 & \mbox{ if } x \in [\beta,\gamma] \\
0 & \mbox{ if } x > \delta \vee x < \alpha \\
\frac{x-\alpha}{\beta - \alpha} & \mbox{ if } x \in [\alpha,\beta[ \\
\frac{\delta -x}{\delta - \gamma} & \mbox{ if } x \in ]\gamma,\delta] \\
\end{cases}
\end{align}

\begin{samepage}
\vspace*{13pt}
\begin{center}
{
\includegraphics[scale=0.25]{./graphs/trapezoidalDistribution.pdf}

}
\end{center}
%\centerline{ \psfig{file=./graphs/Y-time-point.eps}}
\vspace*{10pt}
\fcaption{\label{fig:trapezoidal-dist}Example of fuzzy interval.}
%  \label{fig:fuzzy-validity-period}
\vspace*{13pt}
\end{samepage}

%\def\JPicScale{0.5}
%\begin{figure}[h!]
%  \centering
%  \input{./graphs/trapezoidal.tex}
%  \caption{Trapezoidal membership function}
%  \label{fig:trapezoidal}
%\end{figure}

The representation for a triangular possibility distribution is given by three values $\left[D,a,b \right]$. The distribution is obtained from a trapezoidal possibility distribution by replacing the values $\left[D-a, D, D, D+b \right]$.

% The most convenient form of the membership function of a fuzzy number is a triangular form. It can be shown that such a membership function $\mu_M$ for a fuzzy number $M$ is convex and normalized. Three real values, denoted by $a$, $b$ and $D$, suffice to represent a triangular membership function of a fuzzy number and in this work, a fuzzy number defined as such will be noted as $\left[D, a, b \right]$. Here:
% \begin{itemize}
% \item
% $D$ denotes the single value in the core of $M$
% \item
% $D-a$ is then $\inf \{u \in \mathbb{R} : \mu_{M}(u) > 0\}$
% \item
% $D+b$ is then $\sup \{u \in \mathbb{R} : \mu_{M}(u) > 0\}$
% \end{itemize}
% 
% The membership function of such a fuzzy number is then given by:
% 
% \vspace{-10pt}
% 
% \begin{align}
% \mu_M :   \mathbb{R} \rightarrow \left[0,1\right] :  x \rightarrow \nonumber\\
% \begin{cases}
% \nonumber
% 0 & \mbox{ if } \left(x < D-a\right) \vee \left(x > D+b\right) \\
% \frac{\left[x-\left(D-a\right)\right]}{a} & \mbox{ if } \left(x \geq D-a\right) \wedge (x \leq D)  \\
% -\frac{\left[x-\left(D+b\right)\right]}{b} & \mbox{ if } \left(x \geq D\right) \wedge (x \leq D+b)
% \end{cases}
% \end{align}

%\begin{figure}[h!]
%  \centering
%  \input{./graphs/triangular.tex}
%  \caption{Triangular membership function.}
%  \label{fig:triangular}
%\end{figure}

\subsection{\label{subsec:interval-evaluation-by-ill-known-constraints}Interval Evaluation by Ill-known Constraints}
In our case, we need to know if all points in a crisp interval $I$ reside between the boundaries of an ill-known interval $\left[ X , Y \right]$. To compute that, we introduce the concept of \emph{ill-known constraint}\cite{Pons2011}.

\begin{definition}
Given a universe $U$, an ill-known constraint $C$ on a set $A \subseteq U$ is specified by means of a binary relation $R \subseteq U^{2}$ and a fixed ill-known value denoted by its possibilistic variable $V$ over $U$, i.e.:
\begin{align}
\label{eq:ill-known-constraint}
C \triangleq (R,V)
\end{align}
Set $A$ satisfies the constraint if and only if:
\begin{align}
\forall a \in A : (a,V) \in R
\end{align}
\end{definition}

@@

\begin{samepage}
\vspace*{13pt}
\begin{center}
{
\includegraphics[scale=1]{./graphs/example-ill-known.pdf}
}
\end{center}
%\centerline{ \psfig{file=./graphs/Y-time-point.eps}}
\vspace*{10pt}
\fcaption{\label{fig:example-ill-known}Example of the evaluation of the ill-known constraint $C \triangleq (\leq, X), X = \left[5, 3, 2\right]$. Possibility and necessity measures are shown in grey. }
%  \label{fig:fuzzy-validity-period}
\vspace*{13pt}
\end{samepage}

@@

There is a special boolean combination of constraints that is of particular interest; let us see it.
\begin{definition}
\emph{Conjunctive combination of ill-known constraints}. Consider a universe $U$. Let $R_1, R_2$ be two binary relations in U. Let $X_1, X_2$ be two fixed ill-known values in $U$. Let  $C_1 = (R_1, X_1)$ and $C_2 = (R_2, X_2)$ be two ill-known constraints. A conjunctive combination of both constraints is given by:
\begin{align}
\label{eq:convex-combination}
CC \triangleq \left \lbrace C_1 \wedge C_2 \right \rbrace
\end{align}
In a more general way, it is possible to define the conjunctive combination of an n-ary vector of constraints:
\begin{align}
\label{eq:nary-convex-combination}
CC \triangleq \left \lbrace C_1 \wedge \ldots \wedge C_n \right \rbrace
\end{align}
\end{definition}

@@

Sometimes, an ill-known value might be specified by a convex combination of ill-known constraints. This allow to define ill-known values by means of relationships with respect to other ill-known points.

@@

\begin{definition}
\label{def:convex-combination-ill-known-constraints}
\emph{Ill-known value defined by conjunctive combination of constraints.}
Consider a universe $U$, $CC \triangleq \left \lbrace C_{1_{Z_1}} \wedge \ldots \wedge C_{n_{Z_n}}  \right \rbrace$ a conjunctive combination of ill-known constraints over the variables $Z_1, \ldots, Z_n$. The uncertainty about the evaluation of an ill-known value $X$ is given by:
\begin{align}
\label{eq:ill-known-value-def-by-const-unc}
X \in \Pow(U):\pi_{X}=\pi_{CC}
\end{align}

@@

\begin{example}
As an example, consider a historical database containing data about diplomatic medieval documents. The starting and ending dates when a diplomatic document was valid, are not precisely known.  Consider now that the time granularity are years. Then $X = \left[1112, 2, 2\right]$ is the starting year for the validity of a document. A new diplomatic document was valid in the year $Y = \left[1118, 2, 1 \right]$. Then, It is possible to obtain $Z$ (the period of time between the starting of both documents) by using a conjunctive combination of constraints.

>>>>

%Introductory text:
In this section, the framework of set evaluation by ill-known constraints \cite{Pons2011} is explained. The section also includes a brief introduction to temporal databases.

@@

%\subsection{\label{subsec:possibility-theory}Possibility Theory}
%Possibility theory is devoted to the handling of incomplete information. In order to capture partial ignorance, two measures are provided: possibility and necessity.
%
%\begin{definition}
%Consider a set of outcomes $\Omega$. Let $\Pow(\Omega)$ denote the powerset of $\Omega$ and let $A$ and $B$ be elements of $\Pow(\Omega)$. A \emph{confidence measure on $\Omega$} is defined by a function
%	\begin{align}
%	g : \Pow(\Omega) & \rightarrow \left[0,1\right]
%	\end{align}
%that satisfies
%	\begin{align}
%	g(\emptyset) &= 0 \\
%	g(\Omega) &= 1 	\label{NormalizationProperty} \\
%	A \subseteq B &\Rightarrow g(A) \leq g(B) \label{MonotonicityProperty}
%	\end{align}
%\end{definition}
%
%Both possibility and necessity measures are special cases of confidence measures.
%
%
%
%\begin{definition}
%Consider a confidence measure $\Pi$ on a set of outcomes $\Omega$. Let $J$ be a countable index set and let $\{ A_{j} | j \in J \wedge A_{j} \subseteq \Omega \}$ be a family of elements of $\Pow(\Omega)$. $\Pi$ is now a \emph{possibility measure on $\Omega$} if it satisfies:
%	\begin{align}
%	\Pi\left(\bigcup_{j \in J} A_{j} \right) = \sup_{j \in J} \Pi(A_{j})
%	\end{align}
%\end{definition}
%
%In this work, the interpretation is as follows. The possibility of an event expresses how plausible the occurrence of the event seems to an observer of the experiment, given the (partial) knowledge of the observer about the experiment.
%
%Information on the possibility of distinct elements of the universe of discourse $\Omega$ can now be given by a \emph{possibility distribution} $\pi$ on $\Omega$, defined by:
%
%\begin{definition}
%Consider a possibility measure $\Pi$ on $\Omega$. A \emph{possibility distribution} $\pi$ on $\Omega$ underlying the possibility measure $\Pi$ is a function defined by:
%	\begin{align}
%	\pi : \Omega \rightarrow \left[0, 1\right] : \pi(u) = \Pi(\{u\})
%	\end{align}
%\end{definition}
%
%\begin{definition}
%Consider a confidence measure $N$ on $\Omega$. Let $J$ be a countable index set and let $\{ A_{j} | j \in J \wedge A_{j} \subseteq \Omega \}$ be a family of elements of $\Pow(\Omega)$. $N$ is a \emph{necessity measure} on $\Omega$ if it satisfies:
%	\begin{align}
%	N\left(\bigcap_{j \in J} A_{j} \right) = \inf_{j \in J} N(A_{j})
%	\end{align}
%\end{definition}
%
%In this work, the interpretation is as follows. The necessity of an event expresses how necessary the occurrence of the event seems to an observer of the experiment, given the (partial) knowledge of the observer about the experiment.
%
%Possibility and necessity measures are dual in the sense that:
%
%\begin{align}
%\forall A \subseteq \Omega : N(A) = 1 - \Pi(\bar{A})
%\end{align}
%
%That is, the degree to which an event is necessary is the extent to which every other possible event is not plausible.
%
%\subsection{\label{subsec:possibilistic-variables}Possibilistic Variables}
%Possibilistic variables rely on possibility theory \cite{Dubois1988a} and are defined as follows \cite{Pons2011}.
%
%\begin{definition}
%\label{def;possibilistic-variable}
%A possibilistic variable $X$ over a universe $U$ is defined as a variable taking exactly one value in $U$, but for which this value is (partially) unknown. Possibility distribution $\pi_X$ on $U$ models the available knowledge about the value $X$ takes; for each $u\in U$, $\pi_X(u)$ represents the possibility that $X$ takes the value $u$. In this work, this possibility is interpreted as a measure of how plausible it is that $X$ takes the value $u$, given (partial) knowledge about the value $X$ takes.
%\end{definition}
%
%The exact value a possibilistic variable takes, which is (partially) unknown, is called an \emph{ill-known value} in this work \cite{Dubois1988a}.
%
%When a possibilistic variable is defined on the powerset $\Pow(U)$ of some universe $U$, the unique value the variable takes will be a crisp set and its possibility distribution on the powerset $\Pow(U)$ will describe the possibility of each crisp subset of $U$ to be the value the variable takes. This exact value (a crisp set) the variable takes, is now called an \emph{ill-known set} \cite{Dubois1988a}.
%
%% It is important to understand the difference between the following two concepts:
%% \begin{itemize}
%% \item
%% A \emph{possibilistic variable} $X$ is bounded to take only one value , but this value is not known due to incomplete knowledge. 
%% \item
%% An \emph{ill-known set}~\cite{Dubois1988a}: a possibilistic variable defined over the universe $\Pow(U)$.
%% \end{itemize}
%
%Note that while a single ill-known value refers to one (partially) unknown value, an ill-known set is a crisp set but, for some reason, (partially) unknown.
%
%A specific application of possibilistic variables is obtained when the universe under consideration is the set of Boolean values $\mathbb{B}$ = $\{T,F\}$. Indeed, any Boolean proposition $p$ takes just one value in $\mathbb{B}$. If the knowledge about which value this proposition $p$ will take is given by a possibility distribution $\pi_p$; the proposition can be seen as a possibilistic variable. The possibility and necessity that $p$ = $T$ (the proposition holds) demand more attention. This possibility and necessity are noted here as:
%\begin{align}
%\label{propholdsposs}
%\text{Possibility that $p$ = $T$ (p holds):} &\\
%\nonumber
%Pos(p) = \pi_p(T)  \\
%\label{propholdsnecc}
%\text{Necessity that $p$ = $T$ (p holds):} & \\
%\nonumber
%Nec(p) = 1-\pi_p(F) 
%\end{align}
%
%Here, equation \eqref{propholdsposs} denotes the possibility that $p$ = $T$ and the proposition holds, while equation \eqref{propholdsnecc} denotes the necessity that $p$ = $T$ and the proposition holds.
%
%This work deals with ill-known intervals. These are ill-known sets, defined and represented via a starting and ending points that, in turn, are ill-known values. The elements of the set are the values between the starting and ending points. A closed ill-known interval with starting point defined by possibilistic variable $X$ and ending point by possibilistic variable $Y$ is noted  $\left[X, Y\right]$ here. %The correspondences and transitions between the representations of ill-known sets, between the representations of ill-known intervals and between the representations of an ill-known set and an ill-known interval are part of the authors current research.
%
%\subsection{\label{subsec:fuzzy-numbers}Fuzzy Numbers and Fuzzy Intervals}
%Among others, Dubois and Prade~\cite{Dubois1983} use fuzzy sets \cite{Zadeh1965} to define a \emph{fuzzy interval}:
%\begin{definition}
%A fuzzy interval is a fuzzy set $M$, defined by a membership function $\mu_{M}$ on the set of real numbers $\mathbb{R}$ such that:
%\begin{eqnarray}
%\mu_{M} :  \mathbb{R} \rightarrow \left[0,1\right]  \\ 
%\nonumber
%\forall (u,v)\in\mathbb{R}^2: \forall w \in [u,v]:\\
%\nonumber
%\mu_M(w) \geq\min(\mu_M(u),\mu_M(v))  \\
%\nonumber
%\exists m \in \mathbb{R} :  \mu_M(m)=1 
%\end{eqnarray}
%\end{definition}
%
%\begin{samepage}
%\vspace*{13pt}
%\begin{center}
%{
%\includegraphics[scale=0.25]{./graphs/triangular.pdf}
%
%}
%\end{center}
%%\centerline{ \psfig{file=./graphs/Y-time-point.eps}}
%\vspace*{10pt}
%\fcaption{\label{fig:triangular-dist}Example of fuzzy number.}
%%  \label{fig:fuzzy-validity-period}
%\vspace*{13pt}
%\end{samepage}
%If this modal value $m$ is unique, then $M$ is referred to as a \emph{fuzzy number}. 
%%In other words, if the core of a fuzzy interval is a singleton, it is referred to as a fuzzy number (Figure \ref{fig:triangular-dist}).
%
%A simple form of the membership function of a fuzzy interval is a trapezoidal function (Figure \ref{fig:trapezoidal-dist}). It can be shown that such a membership function $\mu_T$ for a fuzzy interval $T$ is convex and normalized. The values $\left[\alpha, \beta, \gamma, \delta\right]$ represent a trapezoidal possibility distribution defined by $\mu_T$:
%
%% Four real values, denoted $\alpha$, $\beta$, $\gamma$ and $\delta$ suffice to represent a trapezoidal membership function of a fuzzy interval. In this work, a fuzzy interval defined as such will be noted as . The corresponding membership function definition for this  is then given by:
%
%\begin{align}
%\mu_T : & \quad \mathbb{R} \rightarrow \left[0,1\right] \\
%\nonumber
% : & \quad x \rightarrow
%\begin{cases}
%1 & \mbox{ if } x \in [\beta,\gamma] \\
%0 & \mbox{ if } x > \delta \vee x < \alpha \\
%\frac{x-\alpha}{\beta - \alpha} & \mbox{ if } x \in [\alpha,\beta[ \\
%\frac{\delta -x}{\delta - \gamma} & \mbox{ if } x \in ]\gamma,\delta] \\
%\end{cases}
%\end{align}
%
%\begin{samepage}
%\vspace*{13pt}
%\begin{center}
%{
%\includegraphics[scale=0.25]{./graphs/trapezoidalDistribution.pdf}
%
%}
%\end{center}
%%\centerline{ \psfig{file=./graphs/Y-time-point.eps}}
%\vspace*{10pt}
%\fcaption{\label{fig:trapezoidal-dist}Example of fuzzy interval.}
%%  \label{fig:fuzzy-validity-period}
%\vspace*{13pt}
%\end{samepage}
%
%%\def\JPicScale{0.5}
%%\begin{figure}[h!]
%%  \centering
%%  \input{./graphs/trapezoidal.tex}
%%  \caption{Trapezoidal membership function}
%%  \label{fig:trapezoidal}
%%\end{figure}
%
%
%The representation for a triangular possibility distribution is given by three values $\left[D,a,b \right]$. The distribution is obtained from a trapezoidal possibility distribution by replacing the values $\left[D-a, D, D, D+b \right]$.
%
%
%% The most convenient form of the membership function of a fuzzy number is a triangular form. It can be shown that such a membership function $\mu_M$ for a fuzzy number $M$ is convex and normalized. Three real values, denoted by $a$, $b$ and $D$, suffice to represent a triangular membership function of a fuzzy number and in this work, a fuzzy number defined as such will be noted as $\left[D, a, b \right]$. Here:
%% \begin{itemize}
%% \item
%% $D$ denotes the single value in the core of $M$
%% \item
%% $D-a$ is then $\inf \{u \in \mathbb{R} : \mu_{M}(u) > 0\}$
%% \item
%% $D+b$ is then $\sup \{u \in \mathbb{R} : \mu_{M}(u) > 0\}$
%% \end{itemize}
%% 
%% The membership function of such a fuzzy number is then given by:
%% 
%% \vspace{-10pt}
%% 
%% \begin{align}
%% \mu_M :   \mathbb{R} \rightarrow \left[0,1\right] :  x \rightarrow \nonumber\\
%% \begin{cases}
%% \nonumber
%% 0 & \mbox{ if } \left(x < D-a\right) \vee \left(x > D+b\right) \\
%% \frac{\left[x-\left(D-a\right)\right]}{a} & \mbox{ if } \left(x \geq D-a\right) \wedge (x \leq D)  \\
%% -\frac{\left[x-\left(D+b\right)\right]}{b} & \mbox{ if } \left(x \geq D\right) \wedge (x \leq D+b)
%% \end{cases}
%% \end{align}
%
%%\begin{figure}[h!]
%%  \centering
%%  \input{./graphs/triangular.tex}
%%  \caption{Triangular membership function.}
%%  \label{fig:triangular}
%%\end{figure}
%

\subsection{\label{subsec:interval-evaluation-by-ill-known-constraints}Interval Evaluation by Ill-known Constraints}
In our case, we need to know if all points in a crisp interval $I$ reside between the boundaries of an ill-known interval $\left[ X , Y \right]$, where X e Y are possibilistic variables represented by triangular possibility distributions \[D,a,b\], where D is the modal value and a and b are the left and right spreads respectively. To compute that, we introduce the concept of \emph{ill-known constraint}\cite{Pons2011}.

\begin{definition}
Given a universe $U$, an ill-known constraint $C$ on a set $A \subseteq U$ is specified by means of a binary relation $R \subseteq  \tilde\Pow(U)^{2}$ and a fixed ill-known value denoted by its possibilistic variable $V$ over $U$, i.e.:
\begin{align}
\label{eq:ill-known-constraint}
C \triangleq (R,V)
\end{align}
Set $A$ satisfies the constraint if and only if:
\begin{align}
\forall a \in A : (a,V) \in R
\end{align}
\end{definition}

@@

\begin{samepage}
\vspace*{13pt}
\begin{center}
{
\includegraphics[scale=1]{./graphs/example-ill-known.pdf}
}
\end{center}
%\centerline{ \psfig{file=./graphs/Y-time-point.eps}}
\vspace*{10pt}
\fcaption{\label{fig:example-ill-known}Example of the evaluation of the ill-known constraint $C \triangleq (\leq, X), X = \left[5, 3, 2\right]$.  }
%  \label{fig:fuzzy-validity-period}
\vspace*{13pt}
\end{samepage}

@@

There is a special boolean combination of constraints that is of particular interest; let us see it.
\begin{definition}
\emph{Conjunctive combination of ill-known constraints}. Consider a universe $U$. Let $R_1, R_2$ be two binary relations in  $\tilde\Pow(U)$. Let $X_1, X_2$ be two fixed ill-known values in $U$. Let  $C_1 = (R_1, X_1)$ and $C_2 = (R_2, X_2)$ be two ill-known constraints. A conjunctive combination of both constraints is given by:
\begin{align}
\label{eq:convex-combination}
CC \triangleq \left \lbrace C_1 \wedge C_2 \right \rbrace
\end{align}
In a more general way, it is possible to define the conjunctive combination of an n-ary vector of constraints:
\begin{align}
\label{eq:nary-convex-combination}
CC \triangleq \left \lbrace C_1 \wedge \ldots \wedge C_n \right \rbrace
\end{align}
\end{definition}

@@

Sometimes, an ill-known value might be specified by a convex combination of ill-known constraints. This allows to define ill-known values by means of relationships with respect to other ill-known points.

@@

\begin{definition}
\label{def:convex-combination-ill-known-constraints}
\emph{Ill-known value defined by conjunctive combination of constraints.}
Consider a universe $U$, $CC \triangleq \left \lbrace C_{1_{Z_1}} \wedge \ldots \wedge C_{n_{Z_n}}  \right \rbrace$ a conjunctive combination of ill-known constraints over the variables $Z_1, \ldots, Z_n$. The uncertainty about the evaluation of an ill-known value $X$ is given by:
\begin{align}
\label{eq:ill-known-value-def-by-const-unc}
X \in \tilde\Pow(U):\pi_{X}=\pi_{CC}
\end{align}

@@

\begin{example}
As an example, consider a historical database containing data about diplomatic medieval documents. The starting and ending dates when a diplomatic document was valid, are not precisely known.  Consider now that the time granularity are years. Then $X = \left[1112, 2, 2\right]$ is the starting year for the validity of a document. A new diplomatic document was valid in the year $Y = \left[1118, 2, 1 \right]$. Then, it is possible to obtain $Z$ (the period of time between the starting of both documents) by using a conjunctive combination of constraints.
